\thetitle

### 2020-11-20 writing/sample.tex
reivising rational and sample for the new stats

The mutators from section~\ref{sec:mutate} generate 96,515,744 debugging
scenarios; far too many to even identify the interesting ones among them.
Furthermore this population is heterogeneous; different scenarios come
from different mutants and different mutants are the result of a
different mutator and benchmark pair. Hence, to make the experiment
computationally feasible and statistically precise, we perform stratified
uniform random sampling with two levels of stratification.  The first
stratum is the set of mutants and we randomly select from the mutants of
each benchmark.  Our selection of mutants ensures that, per
benchmark, the sample reflects the diversity of mutants with respect to
the mutators that generated them.  Specifically,  we sample 80 mutants
with interesting scenarios per benchmark,  evenly-distributed across all
of the mutators that contribute mutants for the benchmark.  The second
stratum of our sampling is the lattice of a mutant and we draw 96 random
interesting scenarios from each lattice. For lattices that have less than
96 interesting scenarios, we select them all.

In summary, our sampling process takes advantage of ancillary information
to deliver a representative sufficiently large set of scenarios. As a result we test each
mode of the rational programmer on 72,192 randomly selected interesting
debugging scenarios spread across both benchmarks and mutators.
Furthermore stratified random sampling allows us to derive conclusions
about the proportions of the whole population from the proportions of
our sample, exactly what we need to project comparisons about the
usefulness of various modes of the
rational programmer from the sample to set of all interesting debugging
scenarios.  Finally, we can also provide separate estimates per stratum and provide different
viewpoints of our results. For instance, because of the size of the sample
of scenarios from the lattice of a mutant, we can estimate whether natural
blame is more useful than natural exceptions for all interesting scenarios
of each mutant separately with 95\% confidence and 5\% error margin.

>>>>

The mutators from section~\ref{sec:mutate} generate 96,515,744 debugging
scenarios; far too many to even identify the interesting ones among them.
Furthermore this population is heterogeneous; different scenarios come
from different mutants and different mutants are the result of a
different mutator and benchmark pair. Hence, to make the experiment
computationally feasible and statistically precise, we perform stratified
uniform random sampling with three levels of stratification.  The first
two strata group mutants first by benchmark and then by mutator. 
We randomly select from the mutants of
each benchmark ensuring that, per
benchmark, the sample reflects the diversity of mutants with respect to
the mutators that generated them.  Specifically,  we sample 80 mutants
with interesting scenarios per benchmark,  evenly-distributed across all
of the mutators that contribute mutants for the benchmark.  The third
stratum of our sampling is the lattice of a mutant and we draw 96 random
interesting scenarios from each lattice. For lattices that have less than
96 interesting scenarios, we select them all.

In summary, our sampling process takes advantage of ancillary information
to deliver a representative sufficiently large set of scenarios. As a result we test each
mode of the rational programmer on 72,192 randomly selected interesting
debugging scenarios spread across both benchmarks and mutators.
Furthermore stratified random sampling allows us to derive conclusions
about the proportions of the whole population from the proportions of
our sample despite the population's heterogeneity, exactly what we need to project comparisons about the
usefulness of various modes of the
rational programmer from the sample to the set of all interesting debugging
scenarios.  Finally, we can also calculate separate estimates per stratum and provide different
viewpoints of our results. For instance, because of the size of the sample
of scenarios from the lattice of a mutant, we can estimate whether natural
blame is more useful than natural exceptions for all interesting scenarios
of each mutant with 95\% confidence and 5\% error margin.
